---
title: "SCE4 with coordinate selection "
author: "Zilan Chai"
date: "2/17/2022"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(dplyr)
library(data.table)
library(ggplot2) 
library(haven)
library(dplyr)
library(readstata13) 
library(corrplot)
library(mice)
library(pastecs)
#library(bkmr) 
library(knitr)

setwd("/Users/zilanchai/Docs/FinalSimSettings/SCE4_corsel")
sim_popn <- readRDS("popn_highcor_nonlinearLY_3_binary_probit.rds")  
 
```


+ sample size: n = 500
+ MCMC iteration: 12k for all 2 models (L1, Y)
+ Low Variance. 
+ High Correlation.  
+ 3 Metals
+ Nonlinear effect on Y. 

# 1. Generate a simple 1M population 
 
$$L = 0.25*logM_{1,0} + 0.25*\text{wasit}_0 + \epsilon\\
Y = logit^{-1} (1 + 0.1*(\text{sex}-1)^2 + 0.25*(logM_{1,0}-1)^2 + 0.25*logM_{2,1} + 0.25*(\text{waist}_1-1)^2 + \frac{1}{3} * (logM_{2,1}-1) *(\text{waist}_1 -1)  + \epsilon)$$


```{r eval = FALSE}
rm(list = ls())

library(SimDesign)
library(dplyr)
library(gfoRmula)
library(corrplot)

popN = 1000000
k = popN
#covmat <-  toeplitz(c(1, .2, .1))
covmat <-  toeplitz(c(1, .3, .2))

sigsq.trueL = 1
sigsq.trueY = 1 

set.seed(1)


dat <- list(At0 = rmvnorm(k, rep(0,ncol(covmat)), sigma = covmat))
colnames(dat$At0) <- paste("At0_",1:ncol(covmat),sep="") 

dat$sex = rbinom(k, 1, 0.5)
dat$C0 = rnorm(k, mean = 0.25*(1-dat$sex) , 1)

# cor(dat$At1)

dat$epsL <- rnorm(k, sd=sqrt(sigsq.trueL))
dat$epsY <- rnorm(k, sd=sqrt(sigsq.trueY))

hfunL = function(z, ind1 = 1 ,ind2 = 4) 1/4*z[ind1] + 1/4*z[ind2]
hfunY = function(z, ind1 = 1, ind2 = 5, ind3= 7,ind4= 8)  {
  (1/10*(z[ind1]-1)^2 +1/4*(z[ind2]-1)^2+1/4*z[ind3]+ 1/4*(z[ind4]-1)^2) + 1/3*(z[ind2]-1)*(z[ind3]-1)+1 }

dat$hL   <- apply(cbind(dat$At0,dat$C0), 1, hfunL)
dat$L    <- with(dat, hL + epsL)


# At1_mean = c(1/3*mean(dat$At0[,1])+0.1*mean(dat$C0)+10*mean(dat$L),
#              1/3*mean(dat$At0[,2])+0.1*mean(dat$C0)+10*mean(dat$L),
#              1/3*mean(dat$At0[,3])+0.1*mean(dat$C0)+10*mean(dat$L))
# dat$At1  = rmvnorm(k, mean =   At1_mean, sigma = covmat)


sigsq.trueA1= .1
dat$hAt1 = cbind(At1_1 = 1/3*dat$At0[,1]^2 +1/6*dat$At0[,1]+1/10*dat$C0 + 1/10*dat$L,
                 At1_2 = 1/3*dat$At0[,2]^2 +1/6*dat$At0[,2]+1/10*dat$C0 + 1/10*dat$L,
                 At1_3 = 1/3*dat$At0[,3]^2 +1/6*dat$At0[,3]+1/10*dat$C0 + 1/10*dat$L)
dat$epsAt1 <- rnorm(k,  sd=sqrt(sigsq.trueA1))
dat$At1    <- with(dat, hAt1 + epsAt1)
colnames(dat$At1) <- paste("At1_",1:ncol(covmat),sep="") 

dat$A0A1L   <- cbind(dat$At0,dat$At1,dat$L,dat$sex, dat$C0) 

dat$hY   <- apply(dat$A0A1L, 1, hfunY ) 
#  dim(dat$A0A1L)
dat$z    <- with(dat, hY + epsY)
dat$y <- rbinom (popN, 1, pnorm(dat$z))



dat$data <- data.frame(with(dat, cbind(sex, C0, At0,At1, L, y)))  



df=dat$data 
df$id = c(1:1000000)
colnames(df) <- c("sex","waist0", 'logM1_0', 'logM2_0' ,'logM3_0', 
                  'logM1_1', 'logM2_1','logM3_1','waist1','Y','id')


t = cor(df)
corrplot(t)
saveRDS(df, "popn_highcor_nonlinearLY_3_binary_probit.rds")
```



### Simulated Population Correlation Matrix

The corrlation between three metals at time point 1 is 0.3, 0.3, 0.2.

The maximum correlation coefficient in this matrix is 0.38.

```{r}
M = cor(sim_popn)
#cor(sim_popn)
corrplot(M, type = "upper")  
```

# 2. Process Simulation Results

```{r include = FALSE} 
SimRes = c()

for (i in 1:500) {
  file = paste0("Sim_res", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   { 
    next  
  }
  temp = read.csv(paste0("Sim_res", i, ".csv"))
  tmp2 = t(temp)[2,]
  SimRes = rbind(SimRes, tmp2)
  
}
 

para_res= c()

for (i in 1:500) {
  file = paste0("para_res", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   {
    next
  }
  temp = read.csv(paste0("para_res", i, ".csv"))
  tmp2 = t(temp)[2,]
  para_res = rbind(para_res, tmp2)

}


#tbl = apply(para_res, 2, mean)
#kable(tbl)
 
gfun <- function(dat_sim){ 
  lm_l1 <-  lm(waist1 ~  as.factor(sex)   +waist0 +
                 logM1_0+logM2_0+logM3_0 , dat = dat_sim)
  
  lm_y <-  glm(Y ~  as.factor(sex)   +waist0 +waist1 +
                logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1 , dat = dat_sim, family  = binomial(link = "probit"))
  
  K = 1000
  
  A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1)
  
  a <-   apply(A, 2, quantile, probs=0.25)
  astar <-   apply(A, 2, quantile, probs=0.75)
  
  # Calculate L_a*
  
  tmp = rbind(c(0, mean(dat_sim$waist0), a[1:3]), 
              c(0, mean(dat_sim$waist0), astar[1:3])) 
  
  
  newdat_l1 = as.data.frame(tmp)
  colnames(newdat_l1) <- c("sex", "waist0", 'logM1_0', 'logM2_0' ,'logM3_0')
  La.true <- predict(lm_l1, newdata = newdat_l1)[1]
  Lastar.true <- predict(lm_l1, newdata = newdat_l1)[2]
  
  sigma.samp   <- summary(lm_l1)$sigma
  
  La.samp      <- La.true     + rnorm(K, sd=sigma.samp) 
  Lastar.samp  <- Lastar.true + rnorm(K, sd=sigma.samp) 
  
  
  YaLa.samp         <- cbind(0, mean(dat_sim$waist0), La.samp,     matrix(a, nrow=K, ncol=length(a), byrow=TRUE))
  YastarLastar.samp <- cbind(0, mean(dat_sim$waist0), Lastar.samp, matrix(astar, nrow=K, ncol=length(a), byrow=TRUE))
  
  newdat_YaLa <- as.data.frame(YaLa.samp)
  colnames(newdat_YaLa) <- c("sex", "waist0",'waist1', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1')
  
  newdat_YastarLastar <- as.data.frame(YastarLastar.samp)
  colnames(newdat_YastarLastar) <- c("sex", "waist0",'waist1', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1')
  
  
  YaLa.pred   <- predict(lm_y, newdata = newdat_YaLa, type = "response")
  YastarLastar.pred <- predict(lm_y, newdata = newdat_YastarLastar, type = "response")
  
  YaLa         <- mean(YaLa.pred)
  YastarLastar <- mean(YastarLastar.pred)
  
  truth_gformula = mean(YastarLastar) - mean(YaLa) 
  return(truth_gformula)
  
}
   

gfuncorrectmodel <- function(dat_sim){
  
  dat_sim <- mutate(dat_sim, waist1_logM2 = waist1*logM2_1,  logM1_0_sq = logM1_0^2,   logM2_1_sq = logM2_1^2)

lm_l1 <-  lm(waist1 ~ waist0 + logM1_0, dat = dat_sim)

lm_y <-  glm(Y ~  as.factor(sex) + waist1 + logM1_0 + logM2_1 + waist1_logM2 + logM1_0_sq + logM2_1_sq, dat = dat_sim, family = binomial(link = "probit"))

A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1)

a <-   apply(A, 2, quantile, probs=0.25)
astar <-   apply(A, 2, quantile, probs=0.75)

# Calculate L_a*

tmp_a = cbind(dat_sim$waist0, a[1]) %>% as.data.frame()
colnames(tmp_a) <- c("waist0", 'logM1_0')

tmp_astar = cbind(dat_sim$waist0, astar[1]) %>% as.data.frame()
colnames(tmp_astar) <- c("waist0", 'logM1_0')
 
La.true <- predict(lm_l1, newdata = tmp_a)
Lastar.true <- predict(lm_l1, newdata = tmp_astar)

K = 1000
sigma.samp   <- summary(lm_l1)$sigma

La.samp      <- La.true     + rnorm(K, sd=sigma.samp) 
Lastar.samp  <- Lastar.true + rnorm(K, sd=sigma.samp) 


YaLa.samp   <- cbind(dat_sim$sex,  La.samp, a[1], a[5], a[5]*La.samp, a[1]^2, a[5]^2)
YastarLastar.samp   <- cbind(dat_sim$sex,  Lastar.samp, astar[1], astar[5], astar[5]*Lastar.samp, astar[1]^2, astar[5]^2)

newdat_YaLa <- as.data.frame(YaLa.samp)
colnames(newdat_YaLa) <- c("sex", 'waist1', 'logM1_0',  'logM2_1', 'waist1_logM2', 'logM1_0_sq', 'logM2_1_sq')

newdat_YastarLastar <- as.data.frame(YastarLastar.samp)
colnames(newdat_YastarLastar) <-  c("sex", 'waist1', 'logM1_0',  'logM2_1', 'waist1_logM2', 'logM1_0_sq', 'logM2_1_sq')


YaLa.pred   <- predict(lm_y, newdata = newdat_YaLa, type="response")
YastarLastar.pred <- predict(lm_y, newdata = newdat_YastarLastar, type="response")

YaLa         <- mean(YaLa.pred)
YastarLastar <- mean(YastarLastar.pred)

gform_correct = mean(YastarLastar) - mean(YaLa) 
return(gform_correct)
} 


n = 500

gform_diff_samp <- rep(NA, 498)
gform_correct_samp <- rep(NA, 498)

for (i in 1:498){
  set.seed(i)
  dat_sim = sim_popn[sample(sim_popn$id, n, replace=F),] 
  gform_diff_samp[i] <- gfun(dat_sim)
  gform_correct_samp[i] <- gfuncorrectmodel(dat_sim)
}  

SimRes[,2] <- gform_diff_samp
SimRes  <- cbind(SimRes, gform_correct_samp) 
```
 
 


# 3.True Effect - 1. Direct Method

```{r cache=TRUE} 
k = 1000000
sigsq.trueL = 1

hfunL = function(z, ind1 = 1 ,ind2 = 4) 1/4*z[ind1] + 1/4*z[ind2]
hfunY = function(z, ind1 = 1, ind2 = 5, ind3= 7,ind4= 8)  {
  (1/10*(z[ind1]-1)^2 +1/4*(z[ind2]-1)^2+1/4*z[ind3]+ 1/4*(z[ind4]-1)^2) + 1/3*(z[ind2]-1)*(z[ind3]-1)+1 }


A <- dplyr::select(sim_popn, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1)

a <-   apply(A, 2, quantile, probs=0.25)
astar <-   apply(A, 2, quantile, probs=0.75)

a_c0 <- cbind(matrix(a, nrow = k, ncol = length(a), byrow = TRUE), sim_popn$waist0)
astar_c0 <- cbind(matrix(astar, nrow = k, ncol = length(a), byrow = TRUE), sim_popn$waist0)

La.true <- apply(a_c0[,c(1:3, 7)], 1, hfunL )
Lastar.true <- apply(astar_c0[,c(1:3, 7)], 1, hfunL )

La      <- La.true     + rnorm(k, sd=sqrt(sigsq.trueL)) 
Lastar  <- Lastar.true + rnorm(k, sd=sqrt(sigsq.trueL)) 


baLa         <- cbind(matrix(a,nrow=k,ncol=length(a),     byrow=TRUE), La, sim_popn$sex, sim_popn$waist0)
bastarLastar <- cbind(matrix(astar,nrow=k,ncol=length(a), byrow=TRUE), Lastar, sim_popn$sex, sim_popn$waist0)
  
YaLa.z         <-  apply(baLa,        1, hfunY)  
YastarLastar.z <-  apply(bastarLastar, 1, hfunY) 

# YaLa.prob <- mean(exp(YaLa.z)/(exp(YaLa.z) + 1))
# YastarLastar.prob <- mean(exp(YastarLastar.z)/(exp(YastarLastar.z) + 1))
 YaLa.prob <- mean(pnorm(YaLa.z))
 YastarLastar.prob <- mean(pnorm(YastarLastar.z))
  
truth_direct = YastarLastar.prob-YaLa.prob
truth_direct

```


### True Effect - 2. Parametric G-formula on population

```{r  cache=TRUE} 
truth_gform = gfuncorrectmodel(sim_popn)
truth_gform
```

# 4.Coverage 
## Coverage for gBKMR

```{r}
diff_True =  -0.0746417
```

```{r}

diff_bkmr_group = c()

 fun <- function(diff_True){
  for (i in 1:500) {
    file_a = paste0("YaLa_", i,".rds")
    path_a = file.path(file_a)
  
  file_astar = paste0("YastarLastar_", i,".rds")
  path_astar = file.path(file_astar)
  
  
  if(file.exists(path_a)==FALSE || file.exists(path_astar)==FALSE ) { 
    next  
  }
  YaLa_temp = readRDS(file_a)
  YastarLastar_temp = readRDS(file_astar)
  diff_tmp = YastarLastar_temp - YaLa_temp 
   
  upper = quantile(diff_tmp, .975) 
  lower = quantile(diff_tmp, .025) 
  t=sum(upper >= diff_True & lower <= diff_True)
  diff_bkmr_group = c(diff_bkmr_group, t) 
} 
coverage = mean(diff_bkmr_group)
return(coverage)
}

coverage_gBKMR = fun(diff_True)
coverage_gBKMR 
``` 
 

## Coverage for LM, gformula, gformula with correct models

```{r}
# function for LM 
lmfun <- function(dat_sim){
lm_model = glm(Y ~  as.factor(sex)   +waist0 +waist1 +
                logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1 , dat = dat_sim,family = "binomial"(link = "probit"))
summary(lm_model)
newdat_25 <- data.frame(  sex = as.factor(0), 
                        logM1_0 = quantile(dat_sim$logM1_0)[2],
                        logM1_1 = quantile(dat_sim$logM1_1)[2], 
                        logM2_0 = quantile(dat_sim$logM2_0)[2],
                        logM2_1 = quantile(dat_sim$logM2_1)[2], 
                        logM3_0 = quantile(dat_sim$logM3_0)[2],
                        logM3_1 = quantile(dat_sim$logM3_1)[2], 
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1) 
)

newdat_75 <- data.frame( sex = as.factor(0), 
                        logM1_0 = quantile(dat_sim$logM1_0)[4],
                        logM1_1 = quantile(dat_sim$logM1_1)[4], 
                        logM2_0 = quantile(dat_sim$logM2_0)[4],
                        logM2_1 = quantile(dat_sim$logM2_1)[4], 
                        logM3_0 = quantile(dat_sim$logM3_0)[4],
                        logM3_1 = quantile(dat_sim$logM3_1)[4], 
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1) )
yhat_lm_25 = predict(lm_model, newdat_25 )
yhat_lm_75 = predict(lm_model, newdat_75 )
diff_lm = yhat_lm_75-yhat_lm_25 
return(diff_lm)  

}

## Bootstarp function
boot <- function(truth, dat_sim, nboot=1000) {
  t <- matrix(NA, nboot, 3)
  for(B in 1:nboot) {
    index <- sample(1:500, replace=T)
    boot.dat <- dat_sim[index,]
    
    t[B, 1] <- gfun(boot.dat)
    t[B, 2] <- gfuncorrectmodel(boot.dat)
    t[B, 3] <- lmfun(boot.dat)
  }
  return(t)
}

```

 
 
```{r cache = TRUE, eval= FALSE}
## Coverage

coverage_gfun_list <- c()
coverage_gfuncorr_list <- c()
coverage_lm_list <- c()

n = 500 
 
for (i in 1:500){
  print(i)
  set.seed(i)
  dat_sim = sim_popn[sample(sim_popn$id, n, replace=F),] 

  t <- boot(diff_true, dat_sim, nboot=1000)
    
  in_gfun <- sum(quantile(t[, 1], 0.975)>= diff_True & quantile(t[, 1], 0.025) <= diff_True)
  in_gfuncorr <- sum(quantile(t[, 2], 0.975)>= diff_True & quantile(t[, 2], 0.025) <= diff_True)
  in_lm <- sum(quantile(t[, 3], 0.975)>= diff_True & quantile(t[, 3], 0.025) <= diff_True)
  
  coverage_gfun_list <- c(coverage_gfun_list, in_gfun)
  coverage_gfuncorr_list <- c(coverage_gfuncorr_list, in_gfuncorr)
  coverage_lm_list <- c(coverage_lm_list, in_lm)
  
  coverage_gfun <- mean(coverage_gfun_list)
  coverage_gfuncorr <- mean(coverage_gfuncorr_list) 
  coverage_lm <- mean(coverage_lm_list)
}  

```
 
 
 
```{r}
ResCov = c()

for (i in 1:500) {
  file = paste0("coverage_single", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   { 
    next  
  }
  temp = read.csv(paste0("coverage_single", i, ".csv"))
  tmp2 = t(temp)[2,]
  ResCov = rbind(ResCov, tmp2)
  
}

  coverage_gfun <- mean(ResCov[,1])
  coverage_gfuncorr <- mean(ResCov[,2]) 
  coverage_lm <- mean(ResCov[,3])

res = c(coverage_gfun, coverage_gfuncorr, coverage_lm)
print(res)
# Print results
```

 
 
 
 
```{r}
res = c(coverage_gfun, coverage_gfuncorr, coverage_lm)
print(res)
# Print results
```

 
### Simulation Results (comparing gBKMR, gformula, LR)
```{r}
colnames(SimRes) <- c("diff_gBKMR", "diff_gform", "diff_lm" , "gform_correct")

est = apply(SimRes, 2, mean)

bias = est - diff_True
var = apply(SimRes, 2, var) 
RelativeBias = bias/diff_True

MSE = bias^2 + var

simulation_res = as.data.frame(rbind(bias, RelativeBias, var, MSE))

colnames(simulation_res) <-c("diff_gBKMR", "diff_gform", "diff_lm", "gform_correct")
kable(simulation_res)



plotbias =  c( diff_gBKMR=simulation_res[1, 1], diff_lm = simulation_res[1, 3], diff_gform = simulation_res[1, 2], gfrom_correct = simulation_res[1, 4], gBKMR_nosel = 0.004764105,gBKMR_group =  0.02946132 )
plotbias =  stack(plotbias)

plotrelbias =  c( diff_gBKMR=simulation_res[2, 1], diff_lm = simulation_res[2, 3], diff_gform = simulation_res[2, 2], gfrom_correct = simulation_res[2, 4],gBKMR_nosel = -0.06382632, gBKMR_group =  -0.3947033 )
plotrelbias =  stack(plotrelbias)

plotvar =  c( diff_gBKMR=simulation_res[3, 1], diff_lm = simulation_res[3, 3], diff_gform = simulation_res[3, 2], gfrom_correct = simulation_res[3, 4],gBKMR_nosel = 0.001351661, gBKMR_group = 0.0007143314)
plotvar =  stack(plotvar)

plotmse =  c( diff_gBKMR=simulation_res[4, 1], diff_lm = simulation_res[4, 3], diff_gform = simulation_res[4, 2], gfrom_correct = simulation_res[4, 4],gBKMR_nosel = 0.001374358, gBKMR_group = 0.001582301)
plotmse =  stack(plotmse)

plotcoverage =  c( diff_gBKMR = coverage_gBKMR , diff_lm = coverage_lm, diff_gform = coverage_gfun, gfrom_correct = coverage_gfuncorr, gBKMR_nosel = 0.988, gBKMR_group =0.812)
plotcoverage =  stack(plotcoverage )


p1 = ggplot(plotbias, aes(x = ind, y = values)) + 
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs( col="method", y="Bias", title="")+
  ylim(-.5,1)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())

p2 = ggplot(plotrelbias, aes(x = ind, y = values)) +
  geom_point(position = position_dodge(width = 0.75),color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs(  col="method", y="Relative Bias", title="")+  scale_color_manual(values = col)+
  ylim(-1,1.2)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())   

p3 = ggplot(plotvar, aes(x = ind, y = values)) +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs(  col="method", y="Variance", title="")+
  ylim(-.1,.12)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())   

p4 = ggplot(plotmse, aes(x = ind, y = values)) +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) +
  labs(  col="method", y="MSE", title="")+  scale_color_manual(values = col)+
  ylim(-.1,1)+ theme(legend.position = "none") + theme_bw()+ geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())    

p5 = ggplot(plotcoverage, aes(x = ind, y = values)) +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) +
  labs(  col="method", y="Coverage", title="")+  scale_color_manual(values = col)+
  ylim(-.1,1)+ theme(legend.position = "none") + theme_bw()+ geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())     

library(cowplot) 
plot_grid(p1,  p2 ,p3, p4, p5, align = "h", axis = "tb",
  nrow = 5
  )

plotbias
plotmse
plotcoverage
#saveRDS(plotbias, file = "scenario2_bias.rds")
#saveRDS(plotmse, file = "scenario2_mse.rds") 
```
 
```{r}
scenario4_bias= plotbias
scenario4_mse = plotmse
scenario4_coverage= plotcoverage
save(scenario4_bias, scenario4_mse, scenario4_coverage, file = "all_plotdat_s4.Rdata" )
```
 

### Check the distribution of the Baseline Covarites

g-BKMR gives accurate estimates of the baseline covariates in both models. 

Estimates for sex, waist0 in Model1 (model for L)

The truth is 0, 0.25
```{r }
para = apply(para_res, 2, mean)

para_l1 = apply(para_res, 2, mean)[1:2] 
para_y = apply(para_res, 2, mean)[3:4]


para_l1 
```

 Estimates for sex, waist0 in Model2 (model for Y)
 
 The truth is  0.25, 0
```{r}
 
para_y
 
#hist(para_res[,2])
#hist(para_res[,3]) 
```

The histogram of the estimates looks normal. (which is good.)

### Check the distribution of the h function estimates
The estimates of h functions seemed close to the truth. 

```{r}

  l1_est_logM1_0 = c(NA, 50)
  l1_est_logM2_0 = c(NA, 50)
  l1_est_logM3_0 = c(NA, 50)
   
  y_est_logM1_0 = c(NA, 50)
  y_est_logM2_0 = c(NA, 50)
  y_est_logM3_0 = c(NA, 50)
  y_est_logM1_1 = c(NA, 50)
  y_est_logM2_1 = c(NA, 50)
  y_est_logM3_1 = c(NA, 50) 
  y_est_waist_1 = c(NA, 50) 
 
 for (i in 1:500) {
  file1 = paste0("risks_singvar_l1_", i,".rds") 
# file2 = paste0("risks_singvar_l2_", i,".rds")  
  file3 = paste0("risks_singvar_y_", i,".rds")  
   path1 = file.path(file1)
         path3 = file.path(file3)
  if(file.exists(path1)==FALSE)   {
    next
  }

     if(file.exists(path3)==FALSE)   {
    next
  }
  df1 = readRDS(file1)
#  df2 = readRDS(file2)
  df3 = readRDS(file3)
  
  l1_est_logM1_0[i] = as.numeric(filter(df1, q.fixed ==0.5, variable == 'logM1_0')[3])
  l1_est_logM2_0[i] = as.numeric(filter(df1, q.fixed ==0.5, variable == 'logM2_0')[3])
  l1_est_logM3_0[i] = as.numeric(filter(df1, q.fixed ==0.5, variable == 'logM3_0')[3])
  
  # l2_est_logM1_1[i] = as.numeric(filter(df2, q.fixed ==0.5, variable == 'logM1_1')[3])
  # l2_est_logM2_1[i] = as.numeric(filter(df2, q.fixed ==0.5, variable == 'logM2_1')[3])
  # l2_est_logM3_1[i] = as.numeric(filter(df2, q.fixed ==0.5, variable == 'logM3_1')[3])  
  # l2_est_waist_1[i] = as.numeric(filter(df2, q.fixed ==0.5, variable == 'waist1')[3])  
  # 
  y_est_logM1_0[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM1_0')[3])
  y_est_logM2_0[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM2_0')[3])
  y_est_logM3_0[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM3_0')[3])  
  
  y_est_logM1_1[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM1_1')[3])
  y_est_logM2_1[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM2_1')[3])
  y_est_logM3_1[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'logM3_1')[3])  
  y_est_waist_1[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'waist1')[3])  
 # y_est_waist_2[i] = as.numeric(filter(df3, q.fixed ==0.5, variable == 'waist2')[3])  
   
 }
```


```{r}  
par(mfrow=c(1,3))
 hist(l1_est_logM1_0)
 hist(l1_est_logM2_0)
 hist(l1_est_logM3_0) 

h_gbkmr_est_l1 <- c(mean(l1_est_logM1_0, na.rm=T), mean(l1_est_logM2_0, na.rm=T),mean(l1_est_logM3_0, na.rm=T))

change_logM1_0 <-quantile(sim_popn$logM1_0, .75) - quantile(sim_popn$logM1_0, .25)
h_truth_l1 <- 1/4*c(change_logM1_0, 0, 0)

df_h_1 <- as.data.frame(rbind(h_gbkmr_est_l1, h_truth_l1))
colnames(df_h_1) <-c("logM1_0", "logM2_0", "logM3_0"  )

kable(df_h_1)

par(mfrow=c(1,4))
 hist(y_est_logM1_1)
 hist(y_est_logM2_1)
 hist(y_est_logM3_1)
 hist(y_est_waist_1) 

  

h_gbkmr_est_y <- c(mean(y_est_logM1_0, na.rm=T), mean(y_est_logM2_0, na.rm=T),mean(y_est_logM3_0, na.rm=T),mean(y_est_logM1_1, na.rm=T), mean(y_est_logM2_1, na.rm=T),mean(y_est_logM3_1, na.rm=T), mean(y_est_waist_1, na.rm=T))

change_logM1_0 <-quantile(sim_popn$logM1_0, .75) - quantile(sim_popn$logM1_0, .25)
change_logM2_1 <-quantile(sim_popn$logM2_1, .75) - quantile(sim_popn$logM2_1, .25)
change_waist_1 <-quantile(sim_popn$waist1, .75) - quantile(sim_popn$waist1, .25)


h_truth_y <- c(1/4*change_logM1_0, 0, 0, 0, 1/4*change_logM2_1  , 0,1/4*change_waist_1)

df_h_y <- as.data.frame(rbind(h_gbkmr_est_y, h_truth_y))
colnames(df_h_y) <-c("logM1_0", "logM2_0", "logM3_0", "logM1_1", "logM2_1", "logM3_1", "waist1"  )
kable(df_h_y) 
```



  
