---
title: "analysis_sce3_corsel"
author: "Zilan Chai"
date: '2022-10-10'
output: 
  html_document:
    code_folding: hide
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(dplyr)
library(data.table)
library(ggplot2) 
library(haven)
library(dplyr)
library(readstata13) 
library(corrplot)
library(mice)
library(pastecs)
#library(bkmr) 
library(knitr)
library(tidyr)

setwd("/Users/zilanchai/Docs/FinalSimSettings/SCE3_corsel")
sim_popn <- readRDS("popn_3t_highconf_quadraticLY.rds")  
 
```


+ sample size: n = 500
+ MCMC iteration: 24k for all 3 models (L1, L2, Y)
+ High confounding effect. 
+ High Correlation.  
+ 3 Metals
+ Nonlinear effect on Y (quadratic). 


  
# 1. Generate a simple 1M population 

$$L_1 = 0.25*logM_{1,0} + 0.5*\text{wasit}_0 + \epsilon\\
L_2 = 0.25*logM_{2,1} + 0.5*\text{wasit}_1  + 0.25*\text{wasit}_1^2+ \epsilon\\ 
Y = 0.25*\text{wasit}_0 + 0.25*logM_{2,1}  + 0.25* logM_{2,2} + 0.5*\text{wasit}_1   + 0.25*\text{wasit}_2+
0.25*\text{wasit}_0^2 + 0.5*\text{wasit}_1^2   + 0.25*\text{wasit}_2^2  + \epsilon$$

where $logM_{i,j}$ is the $i^{th}$ metal at the $j^{th}$ time point.
 
 
```{r eval = FALSE}
rm(list = ls())

library(SimDesign)
library(dplyr)
library(gfoRmula)
library(corrplot)


#####LINEAR RELATIONSHIP 

popN = 100000
k = popN
#covmat <-  toeplitz(c(1, .1, .1))
#covmat <-  toeplitz(c(1, .3, .2))

covmat <- matrix(c(1,.05, .2, .05, 1, .1, .2, .1,1), nrow = 3, byrow= T)


sigsq.trueL1 = 1
sigsq.trueL2 = 1
sigsq.trueY = 1 

set.seed(1)


dat <- list(At0 = rmvnorm(k, rep(0,ncol(covmat)), sigma = covmat))
colnames(dat$At0) <- paste("At0_",1:ncol(covmat),sep="") 

dat$sex = rbinom(k, 1, 0.5)
dat$C0 = rnorm(k, mean = 0.25*(1-dat$sex) , 1)

# cor(dat$At1)

dat$epsL1 <- rnorm(k, sd=sqrt(sigsq.trueL1))
dat$epsL2 <- rnorm(k, sd=sqrt(sigsq.trueL2))
dat$epsY <- rnorm(k, sd=sqrt(sigsq.trueY))

hfunL1 = function(z, ind1 = 1 ,ind2 = 4) 1/4*z[ind1] +1/2*z[ind2]  

dat$hL1   <- apply(cbind(dat$At0,dat$C0), 1, hfunL1)
dat$L1    <- with(dat, hL1 + epsL1)


sigsq.trueA1= .05
dat$hAt1 = cbind(At1_1 = 1/3*dat$At0[,1]^2 +1/10*dat$At0[,1]+1/10*dat$C0 + 1/10*dat$L1,
                 At1_2 = 1/3*dat$At0[,2]^2 +1/10*dat$At0[,2]+1/10*dat$C0 + 1/10*dat$L1,
                 At1_3 = 1/3*dat$At0[,3]^2 +1/10*dat$At0[,3]+1/10*dat$C0 + 1/10*dat$L1)
dat$epsAt1 <- rnorm(k,  sd=sqrt(sigsq.trueA1))
dat$At1    <- with(dat, hAt1 + epsAt1)
colnames(dat$At1) <- paste("At1_",1:ncol(covmat),sep="") 


hfunL2 = function(z, ind1 = 2 ,ind2 = 4) 1/4*z[ind1] + 1/2*z[ind2] + 1/4*z[ind2] *z[ind2] 

dat$hL2   <- apply(cbind(dat$At1,dat$L1), 1, hfunL2)
dat$L2    <- with(dat, hL2 + epsL2)


sigsq.trueA2= .05
dat$hAt2 = cbind(At2_1 =  1/9*dat$At1[,1]^2 +  1/10*dat$At1[,1],
                 At2_2 =  1/6*dat$At1[,2]^2 +  1/10*dat$At1[,2]+ 1/3*dat$L2,
                 At2_3 =  1/6*dat$At1[,3]^2 +  1/10*dat$At1[,3])
dat$epsAt2 <- rnorm(k,  sd=sqrt(sigsq.trueA2))
dat$At2    <- with(dat, hAt2 + epsAt2)
colnames(dat$At1) <- paste("At2_",1:ncol(covmat),sep="") 



hfunY = function(z, ind1 = 5, ind2 = 8, ind3= 10,ind4= 11, ind5 = 13)  {
  (1/4*z[ind1] + 1/4*z[ind2]+1/2*z[ind3]+1/4*z[ind3]*z[ind3]+
     1/2*z[ind4]+1/4*z[ind4]*z[ind4]+ 1/4*z[ind5]+ 1/4*z[ind5]*z[ind5] )}



dat$ALL   <- cbind(dat$At0,dat$At1,dat$At2,dat$L1,dat$L2,dat$sex, dat$C0) 

dat$hY   <- apply(dat$ALL, 1, hfunY ) 
#  dim(dat$A0A1L)
dat$y    <- with(dat, hY + epsY)

dat$data <- data.frame(with(dat, cbind(sex, C0, At0,At1,At2, L1, L2, y)))  



df=dat$data 
df$id = c(1:k)
colnames(df) <- c("sex","waist0", 'logM1_0', 'logM2_0' ,'logM3_0', 
                  'logM1_1', 'logM2_1','logM3_1',
                  'logM1_2', 'logM2_2','logM3_2', 'waist1', 'waist2','Y','id')


t = cor(df)
corrplot(t, type="upper")
saveRDS(df, "popn_3t_highconf_quadraticLY.rds")
```


### Simulated Population Correlation Matrix

The corrlation between three metals at time point 1 is 0.2, 0.2, 0.1.

The maximum correlation coefficient in this matrix is 0.65.

```{r}
sim_popn_plt = select(sim_popn, -c("Y", "id"))
M = cor(sim_popn_plt)
#cor(sim_popn)
corrplot(M, type = "upper")  
```

# 2. Process Simulation Results
 
```{r cache= TRUE, include = FALSE} 
SimRes = c()

for (i in 1:500) {
  file = paste0("Sim_res", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   { 
    next  
  }
  temp = read.csv(paste0("Sim_res", i, ".csv"))
  tmp2 = t(temp)[2,]
  SimRes = rbind(SimRes, tmp2)
  
}
 
#SimRes = SimRes[,3:4]

para_res= c()

for (i in 1:500) {
  file = paste0("para_res", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   {
    next
  }
  temp = read.csv(paste0("para_res", i, ".csv"))
  tmp2 = t(temp)[2,]
  para_res = rbind(para_res, tmp2)

}

#tbl = apply(para_res, 2, mean)
#kable(tbl)

gfun <- function(dat_sim){ 
  lm_l1 <-  lm(waist1 ~  as.factor(sex)   +waist0 +
                 logM1_0+logM2_0+logM3_0 , dat = dat_sim)
  
  lm_l2 <-  lm(waist2 ~  as.factor(sex)   +waist0 +
                 logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1 , dat = dat_sim)
  lm_y <-  lm(Y ~  as.factor(sex)   +waist0 +waist1 +
                logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1+logM1_2+logM2_2+logM3_2 , dat = dat_sim)
  
  K = 1000
  
  A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1,  logM1_2, logM2_2, logM3_2)
  
  a <-   apply(A, 2, quantile, probs=0.25)
  astar <-   apply(A, 2, quantile, probs=0.75)
  
  # Calculate L_a*
  
  tmp = rbind(c(0, mean(dat_sim$waist0), a[1:3]), 
              c(0, mean(dat_sim$waist0), astar[1:3])) 
  
  
  newdat_l1 = as.data.frame(tmp)
  colnames(newdat_l1) <- c("sex", "waist0", 'logM1_0', 'logM2_0' ,'logM3_0')
  La.true <- predict(lm_l1, newdata = newdat_l1)[1]
  Lastar.true <- predict(lm_l1, newdata = newdat_l1)[2]
  
  K = 1000
  sigma.samp   <- summary(lm_l1)$sigma
  
  La.samp      <- La.true     + rnorm(K, sd=sigma.samp) 
  Lastar.samp  <- Lastar.true + rnorm(K, sd=sigma.samp) 
  
  
    L2aL1a.samp         <- cbind(0, mean(dat_sim$waist0), La.samp,     matrix(a[1:6], nrow=K, ncol=length(a[1:6]), byrow=TRUE))
  L2astarL1astar.samp <- cbind(0, mean(dat_sim$waist0), Lastar.samp, matrix(astar[1:6], nrow=K, ncol=length(a[1:6]), byrow=TRUE))
  
    newdat_L2aL1a <- as.data.frame(L2aL1a.samp  )
  colnames(newdat_L2aL1a) <- c("sex", "waist0",'waist1', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1')
  
  newdat_L2astarL1astar <- as.data.frame(L2astarL1astar.samp)
  colnames(newdat_L2astarL1astar) <- c("sex", "waist0",'waist1', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1')
  
  L2a.true <- predict(lm_l2, newdata =  newdat_L2aL1a)[1]
  L2astar.true <- predict(lm_l2, newdata = newdat_L2astarL1astar)[2]
  
    sigma.l2.samp   <- summary(lm_l2)$sigma
  
  L2a.samp      <- L2a.true     + rnorm(K, sd=sigma.l2.samp) 
  L2astar.samp  <- L2astar.true + rnorm(K, sd=sigma.l2.samp) 
  

  YaLa.samp         <- cbind(0, mean(dat_sim$waist0), La.samp,  L2a.samp,    matrix(a, nrow=K, ncol=length(a), byrow=TRUE))
  YastarLastar.samp <- cbind(0, mean(dat_sim$waist0), Lastar.samp,L2astar.samp,  matrix(astar, nrow=K, ncol=length(a), byrow=TRUE))
  
  newdat_YaLa <- as.data.frame(YaLa.samp)
  colnames(newdat_YaLa) <- c("sex", "waist0",'waist1', 'waist2', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1', 'logM1_2', 'logM2_2','logM3_2')
  
  newdat_YastarLastar <- as.data.frame(YastarLastar.samp)
  colnames(newdat_YastarLastar) <-c("sex", "waist0",'waist1', 'waist2', 'logM1_0', 'logM2_0' ,'logM3_0', 'logM1_1', 'logM2_1','logM3_1', 'logM1_2', 'logM2_2','logM3_2')
  
  YaLa.pred   <- predict(lm_y, newdata = newdat_YaLa)
  YastarLastar.pred <- predict(lm_y, newdata = newdat_YastarLastar)
  
  YaLa         <- mean(YaLa.pred)
  YastarLastar <- mean(YastarLastar.pred)
  
  diff_gformula = mean(YastarLastar) - mean(YaLa) 
  return(diff_gformula)
  
}


gfuncorrectmodel <- function(dat_sim){
  dat_sim <- mutate(dat_sim, waist0_sq = waist0^2, waist1_sq = waist1^2, waist2_sq = waist2^2)

lm_l1 <-  lm(waist1 ~ waist0 + logM1_0 , dat = dat_sim)
lm_l2 <-  lm(waist2 ~ waist1 + logM2_1+ waist1_sq, dat = dat_sim)
lm_y <-  lm(Y ~   waist0 +waist1 + waist2 + logM2_1 + logM2_2 + waist0_sq + waist1_sq + waist2_sq, dat = dat_sim)

A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1,  logM1_2, logM2_2, logM3_2)

a <-   apply(A, 2, quantile, probs=0.25)
astar <-   apply(A, 2, quantile, probs=0.75)

# Calculate L_a*

tmp_a = cbind(dat_sim$waist0, a[1]) %>% as.data.frame()
colnames(tmp_a) <- c("waist0", 'logM1_0')

tmp_astar = cbind(dat_sim$waist0, astar[1]) %>% as.data.frame()
colnames(tmp_astar) <- c("waist0", 'logM1_0')
L1a.true <- predict(lm_l1, newdata = tmp_a)
L1astar.true <- predict(lm_l1, newdata = tmp_astar)

K = 1000
sigma.samp   <- summary(lm_l1)$sigma

L1a.samp      <- L1a.true     + rnorm(K, sd=sigma.samp) 
L1astar.samp  <- L1astar.true + rnorm(K, sd=sigma.samp) 


L2aL1a.samp         <- cbind(L1a.samp, L1a.samp^2, a[5]) %>% as.data.frame()
L2astarL1astar.samp <- cbind(L1astar.samp, L1astar.samp^2, astar[5]) %>% as.data.frame()

colnames(L2aL1a.samp) <- c("waist1","waist1_sq", 'logM2_1')
colnames(L2astarL1astar.samp) <- c("waist1","waist1_sq", 'logM2_1')

L2a.true <- predict(lm_l2, newdata = L2aL1a.samp)
L2astar.true <- predict(lm_l2, newdata = L2astarL1astar.samp)


sigma.samp2   <- summary(lm_l2)$sigma

L2a.samp      <- L2a.true     + rnorm(K, sd=sigma.samp2) 
L2astar.samp  <- L2astar.true + rnorm(K, sd=sigma.samp2) 


YaLa.samp         <- cbind(a[5], a[8], sim_popn$waist0, L1a.samp, L2a.samp, 
                           sim_popn$waist0^2, L1a.samp^2, L2a.samp^2)  
YastarLastar.samp <- cbind(astar[5], astar[8], sim_popn$waist0, L1astar.samp, L2astar.samp, 
                           sim_popn$waist0^2, L1astar.samp^2, L2astar.samp^2)  

newdat_YaLa <- as.data.frame(YaLa.samp)
colnames(newdat_YaLa) <- c( 'logM2_1','logM2_2', "waist0",'waist1', 'waist2', "waist0_sq",'waist1_sq', 'waist2_sq')

newdat_YastarLastar <- as.data.frame(YastarLastar.samp)
colnames(newdat_YastarLastar) <- c( 'logM2_1','logM2_2', "waist0",'waist1', 'waist2', "waist0_sq",'waist1_sq', 'waist2_sq')


YaLa.pred   <- predict(lm_y, newdata = newdat_YaLa)
YastarLastar.pred <- predict(lm_y, newdata = newdat_YastarLastar)

YaLa         <- mean(YaLa.pred)
YastarLastar <- mean(YastarLastar.pred)

diff_gformula = mean(YastarLastar) - mean(YaLa) 
return(diff_gformula)
  
}

n = 500

gform_diff_samp <- rep(NA, 500)
gform_correct_samp <- rep(NA, 500)

for (i in 1:500){
  set.seed(i)
  dat_sim = sim_popn[sample(sim_popn$id, n, replace=F),] 
  gform_diff_samp[i] <- gfun(dat_sim)
  gform_correct_samp[i] <- gfuncorrectmodel(dat_sim)
}  

SimRes  <- cbind(SimRes, gform_diff_samp, gform_correct_samp) 
```
 
# 3. True Effect - Direct Method

```{r cache = TRUE} 
k = 1000000
sigsq.trueL = .25
sigsq.trueL1 = .25
sigsq.trueL2 = .25 


hfunL1 = function(z, ind1 = 1 ,ind2 = 4) 1/4*z[ind1] + 1/2*z[ind2]  

hfunL2 = function(z, ind1 = 2 ,ind2 = 4) 1/4*z[ind1] + 1/2*z[ind2] + 1/4*z[ind2] *z[ind2] 

hfunY = function(z, ind1 = 5, ind2 = 8, ind3= 10,ind4= 11, ind5 = 13)  {
  (1/4*z[ind1] + 1/4*z[ind2]+1/2*z[ind3]+1/4*z[ind3]*z[ind3]+
     1/2*z[ind4]+1/4*z[ind4]*z[ind4]+ 1/4*z[ind5]+ 1/4*z[ind5]*z[ind5] )}

 
A <- dplyr::select(sim_popn, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1,  logM1_2, logM2_2, logM3_2)

a <-   apply(A, 2, quantile, probs=0.25)
astar <-   apply(A, 2, quantile, probs=0.75)

a_c0 <- cbind(matrix(a, nrow = k, ncol = length(a), byrow = TRUE), sim_popn$waist0)
astar_c0 <- cbind(matrix(astar, nrow = k, ncol = length(a), byrow = TRUE), sim_popn$waist0)

L1a.true <- apply(a_c0[,c(1:3, 10)], 1, hfunL1 )
L1astar.true <-  apply(astar_c0[,c(1:3, 10)], 1, hfunL1 )

set.seed(1)

L1a      <- L1a.true     + rnorm(k, sd=sqrt(sigsq.trueL1)) 
L1astar  <- L1astar.true + rnorm(k, sd=sqrt(sigsq.trueL1)) 


baL1a         <- cbind(matrix(a[4:6],nrow=k,ncol=length(a[4:6]),     byrow=TRUE), L1a)
bastarL1astar <- cbind(matrix(astar[4:6],nrow=k,ncol=length(a[4:6]), byrow=TRUE), L1astar)
  
L2aL1a         <- mean(apply(baL1a,         1, hfunL2)) 
L2astarL1astar <- mean(apply(bastarL1astar, 1, hfunL2))

L2a      <- L2aL1a     + rnorm(k, sd=sqrt(sigsq.trueL2)) 
L2astar  <- L2astarL1astar + rnorm(k, sd=sqrt(sigsq.trueL2)) 

ybaL2a         <- cbind(matrix(a,nrow=k,ncol=length(a),     byrow=TRUE), L1a, L2a, sim_popn$sex, sim_popn$waist0)
ybastarL2astar <- cbind(matrix(astar,nrow=k,ncol=length(a), byrow=TRUE), L1astar, L2astar, sim_popn$sex, sim_popn$waist0)

YaLa         <- mean(apply(ybaL2a ,        1, hfunY)) 
YastarLastar <- mean(apply(ybastarL2astar, 1, hfunY))

truth_direct = YastarLastar-YaLa
truth_direct
```

## True Effect - Parametric G-formula with correct model specification on population

```{r cache = TRUE} 
#dat_sim = sim_popn


# dat_sim <- mutate(dat_sim, waist0_sq = waist0^2, waist1_sq = waist1^2, waist2_sq = waist2^2)
# 
# lm_l1 <-  lm(waist1 ~ waist0 + logM1_0 , dat = dat_sim)
# lm_l2 <-  lm(waist2 ~ waist1 + logM2_1+ waist1_sq, dat = dat_sim)
# lm_y <-  lm(Y ~   waist0 +waist1 + waist2 + logM2_1 + logM2_2 + waist0_sq + waist1_sq + waist2_sq, dat = dat_sim)
# 
# A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0,  logM1_1, logM2_1, logM3_1,  logM1_2, logM2_2, logM3_2)
# 
# a <-   apply(A, 2, quantile, probs=0.25)
# astar <-   apply(A, 2, quantile, probs=0.75)
# 
# # Calculate L_a*
# 
# tmp_a = cbind(dat_sim$waist0, a[1]) %>% as.data.frame()
# colnames(tmp_a) <- c("waist0", 'logM1_0')
# 
# tmp_astar = cbind(dat_sim$waist0, astar[1]) %>% as.data.frame()
# colnames(tmp_astar) <- c("waist0", 'logM1_0')
# L1a.true <- predict(lm_l1, newdata = tmp_a)
# L1astar.true <- predict(lm_l1, newdata = tmp_astar)
# 
# K = 1000000
# sigma.samp   <- summary(lm_l1)$sigma
# 
# L1a.samp      <- L1a.true     + rnorm(K, sd=sigma.samp) 
# L1astar.samp  <- L1astar.true + rnorm(K, sd=sigma.samp) 
# 
#  
# L2aL1a.samp         <- cbind(L1a.samp, L1a.samp^2, a[5]) %>% as.data.frame()
# L2astarL1astar.samp <- cbind(L1astar.samp, L1astar.samp^2, astar[5]) %>% as.data.frame()
# 
# colnames(L2aL1a.samp) <- c("waist1","waist1_sq", 'logM2_1')
# colnames(L2astarL1astar.samp) <- c("waist1","waist1_sq", 'logM2_1')
# 
# L2a.true <- predict(lm_l2, newdata = L2aL1a.samp)
# L2astar.true <- predict(lm_l2, newdata = L2astarL1astar.samp)
# 
# 
# sigma.samp2   <- summary(lm_l2)$sigma
# 
# L2a.samp      <- L2a.true     + rnorm(K, sd=sigma.samp2) 
# L2astar.samp  <- L2astar.true + rnorm(K, sd=sigma.samp2) 
# 
# 
# YaLa.samp         <- cbind(a[5], a[8], sim_popn$waist0, L1a.samp, L2a.samp, 
#                            sim_popn$waist0^2, L1a.samp^2, L2a.samp^2)  
# YastarLastar.samp <- cbind(astar[5], astar[8], sim_popn$waist0, L1astar.samp, L2astar.samp, 
#                            sim_popn$waist0^2, L1astar.samp^2, L2astar.samp^2)  
#  
# newdat_YaLa <- as.data.frame(YaLa.samp)
# colnames(newdat_YaLa) <- c( 'logM2_1','logM2_2', "waist0",'waist1', 'waist2', "waist0_sq",'waist1_sq', 'waist2_sq')
# 
# newdat_YastarLastar <- as.data.frame(YastarLastar.samp)
# colnames(newdat_YastarLastar) <- c( 'logM2_1','logM2_2', "waist0",'waist1', 'waist2', "waist0_sq",'waist1_sq', 'waist2_sq')
# 
# 
# YaLa.pred   <- predict(lm_y, newdata = newdat_YaLa)
# YastarLastar.pred <- predict(lm_y, newdata = newdat_YastarLastar)
# 
# YaLa         <- mean(YaLa.pred)
# YastarLastar <- mean(YastarLastar.pred)
# 
# truth_gformula = mean(YastarLastar) - mean(YaLa) 
truth_gformula=  gfuncorrectmodel(sim_popn) 
truth_gformula
```


# 4.Coverage 
## Coverage for gBKMR

```{r}
diff_True = 0.6998381
```

```{r}
diff_bkmr_group = c()

 fun <- function(diff_True){
  for (i in 1:500) {
    file_a = paste0("YaLa_", i,".rds")
    path_a = file.path(file_a)
  
  file_astar = paste0("YastarLastar_", i,".rds")
  path_astar = file.path(file_astar)
  
  
  if(file.exists(path_a)==FALSE || file.exists(path_astar)==FALSE ) { 
    next  
  }
  YaLa_temp = readRDS(file_a)
  YastarLastar_temp = readRDS(file_astar)
  diff_tmp = YastarLastar_temp - YaLa_temp 
   
  upper = quantile(diff_tmp, .975) 
  lower = quantile(diff_tmp, .025) 
  t = sum(upper >= diff_True & lower <= diff_True)
  diff_bkmr_group = c(diff_bkmr_group, t) 
} 
coverage = mean(diff_bkmr_group)
return(coverage)
}

coverage_gBKMR = fun(diff_True)
coverage_gBKMR 
``` 

## Coverage for LM, gformula, gformula with correct models

```{r}
# function for LM 
lmfun <- function(dat_sim){
lm_model = lm(Y ~  as.factor(sex)   +waist0 +waist1 +waist2+
                logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1+logM1_2+logM2_2+logM3_2 , dat = dat_sim)
#summary(lm_model)
newdat_25 <- data.frame(  sex = as.factor(0),
                          logM1_0 = quantile(dat_sim$logM1_0)[2],
                          logM1_1 = quantile(dat_sim$logM1_1)[2],
                          logM1_2 = quantile(dat_sim$logM1_2)[2],
                          logM2_0 = quantile(dat_sim$logM2_0)[2],
                          logM2_1 = quantile(dat_sim$logM2_1)[2],
                          logM2_2 = quantile(dat_sim$logM2_2)[2],
                          logM3_0 = quantile(dat_sim$logM3_0)[2],
                          logM3_1 = quantile(dat_sim$logM3_1)[2],
                          logM3_2 = quantile(dat_sim$logM3_2)[2],
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1),
                        waist2 = mean(dat_sim$waist2)
)

newdat_75 <- data.frame( sex = as.factor(0),
                         logM1_0 = quantile(dat_sim$logM1_0)[4],
                         logM1_1 = quantile(dat_sim$logM1_1)[4],
                         logM1_2 = quantile(dat_sim$logM1_1)[4],
                         logM2_0 = quantile(dat_sim$logM2_0)[4],
                         logM2_1 = quantile(dat_sim$logM2_1)[4],
                         logM2_2 = quantile(dat_sim$logM2_2)[4],
                         logM3_0 = quantile(dat_sim$logM3_0)[4],
                         logM3_1 = quantile(dat_sim$logM3_1)[4],
                         logM3_2 = quantile(dat_sim$logM3_2)[4],
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1) ,
                        waist2 = mean(dat_sim$waist2)
                        )
yhat_lm_25 = predict(lm_model, newdat_25 )
yhat_lm_75 = predict(lm_model, newdat_75 )
diff_lm = yhat_lm_75-yhat_lm_25
return(diff_lm)  

}

## Bootstarp function
boot <- function(truth, dat_sim, nboot=1000) {
  t <- matrix(NA, nboot, 3)
  for(B in 1:nboot) {
    index <- sample(1:500, replace=T)
    boot.dat <- dat_sim[index,]
    
    t[B, 1] <- gfun(boot.dat)
    t[B, 2] <- gfuncorrectmodel(boot.dat)
    t[B, 3] <- lmfun_3t(boot.dat)
  }
  return(t)
}

```

```{r cache=TRUE, eval=FALSE}
## Coverage

coverage_gfun_list <- c()
coverage_gfuncorr_list <- c()
coverage_lm_list <- c()

n = 500 
 
for (i in 1:500){
  print(i)
  set.seed(i)
  dat_sim = sim_popn[sample(sim_popn$id, n, replace=F),] 

  t <- boot(diff_true, dat_sim, nboot=1000)
    
  in_gfun <- sum(quantile(t[, 1], 0.975)>= diff_True & quantile(t[, 1], 0.025) <= diff_True)
  in_gfuncorr <- sum(quantile(t[, 2], 0.975)>= diff_True & quantile(t[, 2], 0.025) <= diff_True)
  in_lm <- sum(quantile(t[, 3], 0.975)>= diff_True & quantile(t[, 3], 0.025) <= diff_True)
  
  coverage_gfun_list <- c(coverage_gfun_list, in_gfun)
  coverage_gfuncorr_list <- c(coverage_gfuncorr_list, in_gfuncorr)
  coverage_lm_list <- c(coverage_lm_list, in_lm)
  
  coverage_gfun <- mean(coverage_gfun_list)
  coverage_gfuncorr <- mean(coverage_gfuncorr_list) 
  coverage_lm <- mean(coverage_lm_list)
}  

```





```{r}
ResCov = c()

for (i in 1:500) {
  file = paste0("coverage_single", i,".csv")
  path = file.path(file)
  if(file.exists(path)==FALSE)   { 
    next  
  }
  temp = read.csv(paste0("coverage_single", i, ".csv"))
  tmp2 = t(temp)[2,]
  ResCov = rbind(ResCov, tmp2)
  
}

  coverage_gfun <- mean(ResCov[,1])
  coverage_gfuncorr <- mean(ResCov[,2]) 
  coverage_lm <- mean(ResCov[,3])

res = c(coverage_gfun, coverage_gfuncorr, coverage_lm)
print(res)
# Print results
```




```{r}
res = c(coverage_gfun, coverage_gfuncorr, coverage_lm)
print(res)
# Print results
```


# 5. Simulation Results and plotting (comparing gBKMR, gformula, LR)
```{r fig.width=5} 
 
colnames(SimRes) <- c("diff_gBKMR", "diff_lm" , "diff_gform", "gform_correct")

est = apply(SimRes, 2, mean)

bias = est - diff_True
var = apply(SimRes, 2, var) 
RelativeBias = bias/diff_True

MSE = bias^2 + var

simulation_res = as.data.frame(rbind(bias, RelativeBias, var, MSE))

colnames(simulation_res) <-c("diff_gBKMR", "diff_lm" , "diff_gform", "gform_correct")
kable(simulation_res)


colors <- c("black","gray25","gray50","darkorchid4","darkorchid3","dodgerblue4","dodgerblue3","darkseagreen4","darkseagreen3","orange2","firebrick2") 

plotbias =  c( diff_gBKMR=simulation_res[1, 1], diff_lm = simulation_res[1, 2], diff_gform = simulation_res[1, 3], gfrom_correct = simulation_res[1, 4], gBKMR_nosel = -0.1132895, gBKMR_group = 1.189538)
plotbias =  stack(plotbias)

plotrelbias =  c( diff_gBKMR=simulation_res[2, 1], diff_lm = simulation_res[2, 2], diff_gform = simulation_res[2, 3], gfrom_correct = simulation_res[2, 4], gBKMR_nosel = -0.1618796, gBKMR_group = 1.699733)
plotrelbias =  stack(plotrelbias)

plotvar =  c( diff_gBKMR=simulation_res[3, 1], diff_lm = simulation_res[3, 2], diff_gform = simulation_res[3, 3], gfrom_correct =  simulation_res[3, 4], gBKMR_nosel = 0.05668504, gBKMR_group = 0.05660542)
plotvar =  stack(plotvar)

plotmse =  c( diff_gBKMR=simulation_res[4, 1], diff_lm = simulation_res[4, 2], diff_gform = simulation_res[4, 3], gfrom_correct = simulation_res[4, 4], gBKMR_nosel = 0.06951956, gBKMR_group =1.471606)
plotmse =  stack(plotmse)

plotcoverage =  c( diff_gBKMR = coverage_gBKMR , diff_lm = coverage_lm, diff_gform = coverage_gfun, gfrom_correct = coverage_gfuncorr, gBKMR_nosel = 0.9899598, gBKMR_group =0)
plotcoverage =  stack(plotcoverage )


# p1 = ggplot(plotbias, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
#   geom_point(position = position_dodge(width = 0.75)) + labs(x="Methods", col="method", y="Bias", title="")+  scale_color_manual(values = col)+
#   ylim(-1,1)+ theme(legend.position = "none")+ geom_vline(xintercept = c(4.5,8.5), color = "black", size=0.75)+ theme_bw() #+ pretty_plot()

p1 = ggplot(plotbias, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs( col="method", y="Bias", title="")+
  ylim(-.5,1)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())

p2 = ggplot(plotrelbias, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
  geom_point(position = position_dodge(width = 0.75),color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs(  col="method", y="Relative Bias", title="")+  scale_color_manual(values = col)+
  ylim(-1,1.2)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())#+ pretty_plot() #+ pretty_plot()

p3 = ggplot(plotvar, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) + labs(  col="method", y="Variance", title="")+
  ylim(-.1,.12)+ theme(legend.position = "none") + theme_bw() + geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())#+ pretty_plot() #+ pretty_plot()

p4 = ggplot(plotmse, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) +
  labs(  col="method", y="MSE", title="")+  scale_color_manual(values = col)+
  ylim(-.1,1)+ theme(legend.position = "none") + theme_bw()+ geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank())#+ pretty_plot()  #+ pretty_plot()


p5 = ggplot(plotcoverage, aes(x = ind, y = values)) + geom_hline(yintercept=-1, linetype="dashed", color="gray") +
  geom_point(position = position_dodge(width = 0.75), color = c("black","dodgerblue3","darkseagreen4","orange2", "gray25","firebrick2")) +
  labs(  col="method", y="Coverage", title="")+  scale_color_manual(values = col)+
  ylim(-.1,1)+ theme(legend.position = "none") + theme_bw()+ geom_hline(yintercept=0, linetype="dashed", color = "red")+ theme( axis.title.x = element_blank()) #+ pretty_plot()  #+ pretty_plot()

library(cowplot) 
plot_grid(p1,   p4, p5, align = "h", axis = "tb",
  nrow = 3
  )

plotbias
plotmse
plotcoverage

# saveRDS(plotbias, file = "scenario3_bias.rds")
# saveRDS(plotmse, file = "scenario3_mse.rds")
# saveRDS(plotcoverage, file = "scenario3_coverage.rds") 
```
 
 

```{r}
scenario3_bias= plotbias
scenario3_mse = plotmse
scenario3_coverage= plotcoverage
save(scenario3_bias, scenario3_mse, scenario3_coverage, file = "all_plotdat_s3.Rdata" )
```
 
 
# Check credible interval for a few simulations

```{r}
dat_sim = sim_popn[sample(sim_popn$id, 500, replace=F),]   

ggplot(gather(dat_sim[, c('sex','waist0', 'waist1', 'Y', 'logM1_0', "logM2_0", "logM3_0", "logM1_1", "logM2_1", "logM3_1")]), aes(value)) + 
    geom_histogram(bins = 10) + 
    facet_wrap(~key, scales = 'free_x') 
```

```{r}
YaLa <- readRDS("YaLa_450.rds") 
YastarLastar <- readRDS("YastarLastar_450.rds")
  diff_tmp = YastarLastar - YaLa
upper = quantile(diff_tmp, .975) 
  lower = quantile(diff_tmp, .025) 
c(lower, upper)
```
```{r}
YaLa <- readRDS("YaLa_1.rds") 
YastarLastar <- readRDS("YastarLastar_1.rds")
  diff_tmp = YastarLastar - YaLa
upper = quantile(diff_tmp, .975) 
  lower = quantile(diff_tmp, .025) 
c(lower, upper)
```

```{r}
YaLa <- readRDS("YaLa_4.rds") 
YastarLastar <- readRDS("YastarLastar_4.rds")
  diff_tmp = YastarLastar - YaLa
upper = quantile(diff_tmp, .975) 
  lower = quantile(diff_tmp, .025) 
c(lower, upper)
```




# Check the distribution of the Baseline Covarites

g-BKMR gives accurate estimates of the baseline covariates in both models. 

Estimates for sex, waist0 in Model1 (model for L)

The truth is 0, 0.25
```{r }
para = apply(para_res, 2, mean)

para_l1 = apply(para_res, 2, mean)[1:2] 
para_y= apply(para_res, 2, mean)[3:4] 

para_l1 
```

 Estimates for sex, waist0 in Model2 (model for Y)
 
 The truth is  0 , 0
```{r}
 
para_y
 
#hist(para_res[,2])
#hist(para_res[,3]) 
```

The histogram of the estimates looks normal. (which is good.)


# Appendix: Simulation code on cluster

```{r eval = FALSE}
args<-commandArgs(TRUE)
currind <-as.integer(args[1])
print(currind)

library(bkmr)
library(data.table)
library(CBPS)
library(dplyr)

sim_popn = readRDS("popn_3t_highconf_quadraticLY.rds")
n = 500

sel<-seq(22000,24000,by=25)

sim_res = rep(NA, 2)

set.seed(currind)
dat_sim = sim_popn[sample(sim_popn$id, n, replace=F),]


L1 = dat_sim$waist1

Cov_mat_l1 = dplyr::select(dat_sim,   sex,  waist0 )
Exp_mat_l1 = dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0 )



L2 = dat_sim$waist1

Cov_mat_l2 = dplyr::select(dat_sim,   sex,  waist0 )
Exp_mat_l2 = dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0, logM1_1, logM2_1, logM3_1, waist1 )


Y = dat_sim$Y
Cov_mat_y = dplyr::select(dat_sim,  sex,  waist0 )
Exp_mat_y= dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0, logM1_1, logM2_1, logM3_1 ,
                         logM1_2, logM2_2, logM3_2 , waist1, waist2  )


  fitkm_l1 <- kmbayes(y = L1, Z = Exp_mat_l1, X = Cov_mat_l1, iter = 24000, verbose = FALSE, varsel = TRUE)
 saveRDS(fitkm_l1, file = paste0("fitkm_l1_", currind, ".rds"))
 #
 #
 fitkm_l2 <- kmbayes(y = L2, Z = Exp_mat_l2, X = Cov_mat_l2, iter = 24000, verbose = FALSE, varsel = TRUE)
 saveRDS(fitkm_l2, file = paste0("fitkm_l2_", currind, ".rds"))

  fitkm_y <- kmbayes(y = Y, Z = Exp_mat_y, X = Cov_mat_y, iter = 24000, verbose = FALSE, varsel = TRUE)
 saveRDS(fitkm_y, file = paste0("fitkm_y_", currind, ".rds"))

#fitkm_l1 <- readRDS(paste0("fitkm_l1_", currind, ".rds"))
# fitkm_l2 <- readRDS(paste0("fitkm_l2_", currind, ".rds"))
#fitkm_y <- readRDS(paste0("fitkm_y_", currind, ".rds"))

  start.time <- proc.time()
K = 1000

 A <- dplyr::select(dat_sim, logM1_0, logM2_0, logM3_0, logM1_1, logM2_1, logM3_1, logM1_2, logM2_2, logM3_2)

a <-   apply(A, 2, quantile, probs=0.25)
astar <-   apply(A, 2, quantile, probs=0.75)

# Calculate L_a*

X.predict.L <- matrix(colMeans(Cov_mat_l1),nrow=1)
X.predict.Y <- matrix(colMeans(Cov_mat_y),nrow=1)

newz      <- rbind(a,astar)
set.seed(93020)
EL1.samp <- SamplePred(fitkm_l1, Znew =newz[,1:3], Xnew = X.predict.L, sel=sel)
L1a       <- as.vector(EL1.samp[,"znew1"])
L1astar   <- as.vector(EL1.samp[,"znew2"])

sigma.samp   <- sqrt(fitkm_l1$sigsq.eps[sel])
set.seed(93020)
random.samp1 <- matrix(rnorm(length(sel)*K),nrow=length(sel),ncol=K)
random.samp2 <- matrix(rnorm(length(sel)*K),nrow=length(sel),ncol=K)

L1a.samp     <- L1a + sigma.samp*random.samp1
L1astar.samp <- L1astar + sigma.samp*random.samp2


L2aL1a.samp.mat <- matrix(NA,nrow=length(sel),ncol=K)
L2astarL1astar.samp.mat <- matrix(NA,nrow=length(sel),ncol=K)


for(j in 1:length(sel)){
  print(j)
  L1a.j     <- L1a.samp[j,]
  L1astar.j <- L1astar.samp[j,]

  aL1a.j         <- cbind(matrix(a[1:6], nrow=K, ncol=length(a[1:6]), byrow=TRUE), L1a.j)
  astarL1astar.j <- cbind(matrix(astar[1:6], nrow=K, ncol=length(astar[1:6]), byrow=TRUE), L1astar.j)

  for(k in 1:K){
    newz <- rbind(aL1a.j[k,], astarL1astar.j[k,])

    set.seed(j + 10000)
    L2astarL1astar.jk <- SamplePred(fitkm_l2, Znew = newz, Xnew = X.predict.L, sel=sel[j])

    L2aL1a.samp.mat[j,k]<- L2astarL1astar.jk[,"znew1"]
    L2astarL1astar.samp.mat[j,k]<- L2astarL1astar.jk[,"znew2"]

  }
  end.time.temp <- proc.time()
  if(j%%50==0) print(paste("iter", j, "time: ", round((end.time.temp - start.time)["elapsed"]/60,2),"min"))
}


sigma.samp.l2  <- sqrt(fitkm_l2$sigsq.eps[sel])

L2aL1a = as.vector(apply(L2aL1a.samp.mat, 1, mean))
L2astarL1astar = as.vector(apply(L2astarL1astar.samp.mat, 1, mean))

random.samp.l2.1 <- matrix(rnorm(length(sel)*K),nrow=length(sel),ncol=K)
random.samp.l2.2 <- matrix(rnorm(length(sel)*K),nrow=length(sel),ncol=K)

L2aL1a.samp  <- L2aL1a+ sigma.samp.l2*random.samp.l2.1
L2astarL1astar.samp  <- L2astarL1astar+ sigma.samp.l2*random.samp.l2.2


YaLa.samp.mat <- matrix(NA,nrow=length(sel),ncol=K)
YastarLastar.samp.mat <- matrix(NA,nrow=length(sel),ncol=K)


for(j in 1:length(sel)){
  print(j)
  L1a.j     <- L1a.samp[j,]
  L2a.j     <- L2aL1a.samp[j,]
  aLa.j     <- cbind(matrix(a, nrow=K, ncol=length(a), byrow=TRUE), L1a.j, L2a.j)


  L1astar.j     <- L1astar.samp[j,]
  L2astar.j     <- L2astarL1astar.samp[j,]
  astarLastar.j     <- cbind(matrix(astar, nrow=K, ncol=length(astar), byrow=TRUE), L1astar.j, L2astar.j)


  for(k in 1:K){
    newz <- rbind(aLa.j[k,], astarLastar.j[k,])

    set.seed(j + 10000)
    Y.jk <- SamplePred(fitkm_y, Znew = newz, Xnew = X.predict.Y, sel=sel[j])

    YaLa.samp.mat[j,k]<- Y.jk[,"znew1"]
    YastarLastar.samp.mat[j,k]<- Y.jk[,"znew2"]

  }
  end.time.temp <- proc.time()
  if(j%%50==0) print(paste("iter", j, "time: ", round((end.time.temp - start.time)["elapsed"]/60,2),"min"))
}


YaLa         <- apply(YaLa.samp.mat,        1,mean)
YastarLastar <- apply(YastarLastar.samp.mat,1,mean)

saveRDS( YaLa, paste0("YaLa_", currind, ".rds"))
saveRDS( YastarLastar, paste0("YastarLastar_", currind, ".rds"))

##g-BKMR
diff_gBKMR = mean(YastarLastar) - mean(YaLa)

para_l1 = apply(fitkm_l1$beta[22000:24000,],2,mean)
para_l2 = apply(fitkm_l2$beta[22000:24000,],2,mean)
para_y = apply(fitkm_y$beta[22000:24000,],2,mean)
para_l1l2y = c( para_l1,  para_l2, para_y)

write.csv(para_l1l2y, file = paste0("para_res", currind, ".csv"))


##### Linear Regression


# df_lm = dplyr::mutate(dat_sim,
#                       glucose0 = glucose0 - mean(glucose0),
#                        waist0 =  waist0 - mean(waist0), waist1 = waist1 - mean(waist1) ,
#                        age = age - mean(age))



lm_model = lm(Y ~  as.factor(sex)   +waist0 +waist1 +waist2+
                logM1_0+logM2_0+logM3_0+logM1_1+logM2_1+logM3_1+logM1_2+logM2_2+logM3_2 , dat = dat_sim)
#summary(lm_model)
newdat_25 <- data.frame(  sex = as.factor(0),
                          logM1_0 = quantile(dat_sim$logM1_0)[2],
                          logM1_1 = quantile(dat_sim$logM1_1)[2],
                          logM1_2 = quantile(dat_sim$logM1_2)[2],
                          logM2_0 = quantile(dat_sim$logM2_0)[2],
                          logM2_1 = quantile(dat_sim$logM2_1)[2],
                          logM2_2 = quantile(dat_sim$logM2_2)[2],
                          logM3_0 = quantile(dat_sim$logM3_0)[2],
                          logM3_1 = quantile(dat_sim$logM3_1)[2],
                          logM3_2 = quantile(dat_sim$logM3_2)[2],
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1),
                        waist2 = mean(dat_sim$waist2)
)

newdat_75 <- data.frame( sex = as.factor(0),
                         logM1_0 = quantile(dat_sim$logM1_0)[4],
                         logM1_1 = quantile(dat_sim$logM1_1)[4],
                         logM1_2 = quantile(dat_sim$logM1_1)[4],
                         logM2_0 = quantile(dat_sim$logM2_0)[4],
                         logM2_1 = quantile(dat_sim$logM2_1)[4],
                         logM2_2 = quantile(dat_sim$logM2_2)[4],
                         logM3_0 = quantile(dat_sim$logM3_0)[4],
                         logM3_1 = quantile(dat_sim$logM3_1)[4],
                         logM3_2 = quantile(dat_sim$logM3_2)[4],
                        waist0 = mean(dat_sim$waist0),
                        waist1 = mean(dat_sim$waist1) ,
                        waist2 = mean(dat_sim$waist2)
                        )
yhat_lm_25 = predict(lm_model, newdat_25 )
yhat_lm_75 = predict(lm_model, newdat_75 )
diff_lm = yhat_lm_75-yhat_lm_25





sim_res[1] <-  diff_gBKMR
sim_res[2] <- diff_lm

write.csv(sim_res, file = paste0("Sim_res", currind, ".csv"))




risks_singvar_l1 <- SingVarRiskSummaries(fit = fitkm_l1, y = L1, Z = Exp_mat_l1, X = as.matrix(Cov_mat_l1),
                                         qs.diff = c(0.25,0.75),
                                         q.fixed = c( 0.25, 0.5, 0.75),
                                         method = "exact")
saveRDS(risks_singvar_l1, file = paste0("risks_singvar_l1_", currind, ".rds"))


risks_singvar_y <- SingVarRiskSummaries(fit = fitkm_y, y = Y, Z = Exp_mat_y, X = as.matrix(Cov_mat_y),
                                        qs.diff = c(0.25,0.75),
                                        q.fixed = c( 0.25,0.5, 0.75),
                                        method = "exact")

saveRDS(risks_singvar_y, file = paste0("risks_singvar_y_", currind, ".rds"))

```
